Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-04-04 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/paper.tex
Initial version of conclusions was added.

There is a branch in the theory for the formal languages which is related to a context-free grammar (CFG). In such grammar there are set of production rules. Application of these rules lead to generation of all possible strings in a specified formal language. In CFG a production rule is an operation of simple replacement. Rules are applied regardless of the context. The left hand side of a CFG rule is always nonterminal symbol. It means that nonterminal symbols are not part of the resulting string. The right hand side of a CFG rule consists of terminal symbol, nonterminal symbols or combination of both. The main idea in CFGs is that nonterminal symbols are substituted with the given rules until there is no nonterminal symbols in the generated string.

@@

@@

%----------------------------------------------------------------------------------------
%   Bibliography
%----------------------------------------------------------------------------------------
\begin{thebibliography}{99}
\end{thebibliography}

>>>>

There is a branch in the theory for the formal languages which is related to a context-free grammar (CFG). In such grammar there are set of production rules. Application of these rules lead to generation of all possible strings in a specified formal language \cite{ochoa01}. In CFG a production rule is an operation of simple replacement. Rules are applied regardless of the context. The left hand side of a CFG rule is always nonterminal symbol. It means that nonterminal symbols are not part of the resulting string. The right hand side of a CFG rule consists of terminal symbol, nonterminal symbols or combination of both. The main idea in CFGs is that nonterminal symbols are substituted with the given rules until there is no nonterminal symbols in the generated string.

@@

The extension of the idea for fractal generation from 2D to 3D space shows that in 3D space the process is much more time consuming than in the 2D space. Voxel based representation of 3D objects consumes too much computational resources. Generated objects are not applicable in real use, but results achieved are promising for further research of the fractal nature of the world in which all we are living.

@@

%----------------------------------------------------------------------------------------
%   Bibliography
%----------------------------------------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{ochoa01} Ochoa, G., \textit{On Genetic Algorithms and Lindenmayer Systems}, Parallel Problem Solving from Nature, Lecture Notes in Computer Science, vol. 1498, ISBN 978-3-540-65078-2, 335--344, 1998.

\end{thebibliography}
